Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$

### 2015-05-05 formalwriteup.tex
modified dunkl operators proposition

\newcommand{\xx}[1]{\textcolor{blue}{#1}}
\newcommand{\zb}{\overline{z}}
\newcommand{\cc}[1]{\overline{#1}}
\newcommand{\m}[1]{\left|#1\right|}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\p}[1]{\left(#1\right)}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\D}{\triangle}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\f}[1]{\sum_{n=-\infty}^\infty #1_ne^{inx}}
\newcommand{\fn}[1]{\sum_{n=-\infty}^\infty #1e^{inx}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\mm}[1]{\m{\m{#1}}}
\newcommand{\ang}[1]{\left\langle #1 \right\rangle}
\newcommand{\h}{\mathfrak{h}}
\newcommand{\GL}{{\rm GL}}
\newcommand{\HH}{{\rm H}}
\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{{\tt arXiv:#1}}}
\newcommand{\Sym}{\operatorname{Sym}}

\title{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic}

@@

\begin{abstract}
We study lowest-weight irreducible representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ when $p$ divides $n$, $\tau$ is trivial, $\hbar=1$, and $c$ is generic. We describe the generators of kernel of the contravariant bilinear form on the Verma module in terms of a formal power series that is related to the residues that generate the kernel in the characteristic $0$ case; we give a formula for the Hilbert series of the irreducible representation.
\end{abstract}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$.

This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type A (associated to the symmetric group $\Sigma_n$). In general new techniques are required to study positive characteristc as opposed to characteristic 0. In this paper we directly connect the characteristc 0 case to the positive characteristic case; instead of taking complex residues, we consider the coefficients of formal power series in positive characteristic. While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups.

Given the symmetric group $\Sigma_n$ and a representation $\h$ of $\Sigma_n$ over a field $K$, we let $\mathcal{S}$ be the set of transpositions in $\Sigma_n$. For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.

Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$. We choose $\hbar,c \in K$. Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $K[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the following relations for all $x,x' \in \h^*, y,y' \in \h$:
\begin{align*}
[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s.
\end{align*}
We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in K[G]$. We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_K K[\Sigma_n] \otimes_K \Sym(\h^*)$ (\cite{EM}, section 3.2).

In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$. Then we can assume $\hbar=0$ or $\hbar = 1$.

Let $\tau$ be a representation of $G$. The {\it Verma module} $M_{\hbar,c}(\h,\tau)$ is defined as $\HH_{\hbar,c}(\h) \otimes_{K[\Sigma_n] \ltimes \Sym(\h)} \tau$. Using the PBW decomposition of the Cherednik algebra, we see that $M_{\hbar,c}(\h,\tau)=\Sym(\h^*) \otimes_K \tau$ as a $K$-vector space; we can give this a $\mathbb{Z}$-grading in an obvious way. We are concerned with the case $\tau$ trivial, or the {\it polynomial representation} $\Sym(\h^*)$, which is a polynomial ring. We refer to the polynomial representation as $A$.

As described in section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
\begin{align*}
\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
\end{align*}
The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$. The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the $j$-graded factor of $A/J$.

 We call $c$ {\it generic} if we do not specify its value. We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $K$ dividing $n$. We also have $\dim \h = n-1$, so $\h$ is an irreducible representation of the symmetric group. We state our result for this case below:

 \newtheorem*{thm:main}{Theorem \ref{thm:main}}
\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection; it has Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. $J$ is generated by the coefficients of $z^p$ in the formal power series \\
$F_a=\frac{1}{1-x_az} \left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$ for $a=0,\dots,n-2$. 
\end{thm:main}

In this paper we consider the case where the characteristic of $K$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}. In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$. To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$. The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$. We simplify and truncate the formal power series so we can define it in positive characteristic.

@@

To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions. The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $K[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}. For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
\end{align*}

@@

The characteristic of the field $K$ is $p>0$. We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.

\section{Representations of rational Cherednik algebras of $\Sigma_n$ in positive characteristic $p \mid n$}

@@

\begin{proof}
Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations. We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.

We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$. Therefore we need only consider the action of the Dunkl operators on $F_0$. We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators.

We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$. In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$. Then since $p>2$, we note that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$. Therefore we can add multiples of $(g-1)^{p-1}$ when taking the Dunkl operator's action on $F_0$, since even when multipled by another power series it cannot contribute anything to the coefficient of $z^p$. We also note that we can add $n$ times any multiple of $F_0$ since $n \equiv 0 \bmod p$.

Using the allowed manipulations and the fact that $x_{n-1}=-x_0+\dots-x_{n-2}$, we see that up to the $z^p$ coefficient,

\begin{align*}
\frac{\partial F_0}{\partial x_1}=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0, \quad \frac{\partial F_0}{\partial x_0}=\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0.
\end{align*}

We note that when $0 < i,j$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=0$. We also see that for $0 < i \le n-1$ we have $\frac{1-s_{ij}}{x_i-x_j}\left(F_0\right)=\frac{z}{1-x_iz}F_0$.

We also consider $\frac{\partial F_0}{\partial z}$; up to the addition of some multiple of $(g-1)^{p-1}$, this is equal to $\frac{x_0}{1-x_0z}F_0-\sum_{j \ge 0} \frac{-x_jc}{1-x_jz}F_0$.

Then we see that:

\begin{align*}
(D_1-D_0)(F_0)&=\frac{\partial F_0}{\partial x_1}-\frac{\partial F_0}{\partial x_0}-c\frac{1-s_{01}}{x_1-x_0}(F_0)+c\sum_{j>0}\frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\left(\frac{zc}{1-x_{n-1}z}-\frac{zc}{1-x_1z}\right)F_0-\left(\frac{zc}{1-x_{n-1}z}+\frac{z(1-c)}{1-x_1z}\right)F_0+\frac{zc}{1-x_1z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
&=\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0}\frac{zc}{1-x_jz}F_0\\
&=-\frac{z}{1-x_0z}f_0+\sum_{j} \frac{zc}{1-x_jz}f_0\\
&=-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{zc}{1-x_jz}f_0\right)-nzcf_0\\
&=-zf_0+\frac{z-x_0z^2}{1-x_0z}f_0-\frac{z}{1-x_0z}f_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}f_0+\frac{zc}{1-x_jz}f_0\right)\\
&=-zf_0+\frac{-x_0z^2}{1-x_0z}f_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}f_0\right)\\
&=-zf_0-z^2\frac{\partial f_0}{\partial z}.
\end{align*}

Then if $b$ is the coefficient of $z^{p-1}$ in $f_0$, we see that the coefficient of $z^p$ in $-zf_0$ is $-b$, and the coefficient of $z^p$ in $-z^2\frac{\partial f_0}{\partial z}$ is $-(p-1)b=b$. Therefore the coefficient of $z^p$ in $(D_1-D_0)(F_0)$ is $-b+b=0$; this means that $(D_1-D_0)(f_0)=0$.

Then as we discussed above, the symmetry of the $f_a$ means that all the $f_a$ are annihilated by the Dunkl operators, as desired.

>>>>

\newcommand{\xx}[1]{\textcolor{blue}{#1}}
\newcommand{\zb}{\overline{z}}
\newcommand{\cc}[1]{\overline{#1}}
\newcommand{\m}[1]{\left|#1\right|}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\p}[1]{\left(#1\right)}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\D}{\triangle}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\f}[1]{\sum_{n=-\infty}^\infty #1_ne^{inx}}
\newcommand{\fn}[1]{\sum_{n=-\infty}^\infty #1e^{inx}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\mm}[1]{\m{\m{#1}}}
\newcommand{\ang}[1]{\left\langle #1 \right\rangle}
\newcommand{\h}{\mathfrak{h}}
\newcommand{\GL}{{\rm GL}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{{\tt arXiv:#1}}}
\newcommand{\Sym}{\operatorname{Sym}}

\title{Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$}

@@

\begin{abstract}
We study the polynomial representation of the ratioal Cherednik algebra of type $A_{n-1}$ with generic parameter in characteristic $p$ for $p \mid n$. We give explicit formulas for generators for the maximal ideal, show that they cut out a complete intersection, and thus compute the Hilbert series of the irreducible quotient. Our methods are motivated by generalizing from characteristic $0$ to characteristic $p$. \end{abstract}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$). In general new techniques are required to study positive characteristc as opposed to characteristic 0. In this paper we directly connect the characteristc 0 case to the positive characteristic case; instead of taking complex residues, we consider the coefficients of formal power series in positive characteristic. While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

%mention previous results [BEG],[CE],[GLOR]? ask
%deformation of DAHAs introduced by Etingof-Ginzburg in 2001

Given the symmetric group $\Sigma_n$, we let $\mathcal{S}$ be the set of reflections in $\Sigma_n$. Let $\h$ be the irreducible $(n-1)$-dimensional representation of $\Sigma_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$. For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.

Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$. We choose $\hbar,c \in k$. Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the relations
\begin{align*}
[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s
\end{align*}
 for all $x,x' \in \h^*, y,y' \in \h$. We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$. We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[\Sigma_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).

In general, for any $\alpha \ne 0$, $\HH_{\hbar,c}(\h)\simeq \HH_{\alpha\hbar,\alpha c}(\h)$, so we restrict to $\hbar=0$ or $\hbar = 1$.

\subsection{Representations of rational Cherednik algebras}

We are concerned with the {\it polynomial representation} $\Sym(\h^*)$ of $\HH_{\hbar,c}$, which is a polynomial ring. We refer to the polynomial representation as $A$; we can give this a $\mathbb{Z}$-grading in an obvious way.

As described in Section 2.5 of \cite{BC1}, $A=\Sym(\h^*)$ has a unique maximal graded proper submodule $J$ which can be realized as the kernel of the contravariant form $\beta_c: \Sym(\h^*) \times \Sym(\h) \to k$; $\beta_c$ can be characterized by the property that for all $x \in \h^*, y \in \h, f \in \Sym(\h^*), g \in  \Sym(\h)$:
\begin{align*}
\beta_c(xf,g)=\beta_c(f,xg), \quad \beta_c(f,yg) = \beta_c(yf,g), \quad \beta_c(1,1) = 1.
\end{align*}
The quotient $A/J$ is a finite-dimensional irreducible $\mathbb{Z}$-graded representation of $\HH_{\hbar,c}(\h)$. The {\it Hilbert series} $h_{A/J}(t)$ of $A/J$ is $\sum_{j=0}^\infty (\dim_k L_j)t^k$ where $L_j$ is the $j$-graded factor of $A/J$.

\subsection{Main results}

 We call $c$ {\it generic} if we do not specify its value. We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$. We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $\Sigma_n$ of dimension $n-1$. We state our result for this case below:

 \newtheorem*{thm:main}{Theorem \ref{thm:main}}
\begin{thm:main} The irreducible representation $A/J$  of $\HH_{\hbar,c}(\h)$ is a complete intersection with  Hilbert series $\left(\frac{1-t^p}{1-t}\right)^{n-1}$. The maximal ideal $J$ is generated by the coefficients of $z^p$ in the formal power series \\
$$F_a=\frac{1}{1-x_az} \prod_{j=0}^{n-1}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1+\prod_{j=0}^{n-1} (1-x_jz))^k\right)$$ for $a=0,\dots,n-2$. 
\end{thm:main}

We assume $p>2$ since the case $p=2$ is fully characterized in \cite{L}.

\subsection{Connection to characteristic $0$ results}

In this paper we consider the case where the characteristic of $K$ divides $n$. This is related to the case in characteristic $0$ where $c$ takes the specific value $p/n$, as described in \cite{CE}. In that case the generators of the ideal $J$ were the residues at infinity of $\frac{1}{z-x_a} \prod_{i=0}^{n-1} (z-x_i)^c$ for each $a$. %write as proposition
To get a similar result in positive characteristic, we must consider formal power series in $z$ with coefficients from $A$. The formal power series would be $\frac{1}{z^{p+1}}\frac{1}{1-x_az}\prod_{j=0}^{n-1} (1-x_jz)^c$, with the corresponding generator as the coefficient of $1/z$. We simplify and truncate the formal power series so we can define it in positive characteristic.

\subsection{Relation to previous work}

%fill in?

@@

 \section{The rational Cherednik algebra}

 \subsection{Dunkl operators}

To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions. The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}. For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
\end{align*}

@@

\section{Proof of the main result}

@@

\begin{proof}
%Taking the Dunkl operator of an element of $A$ consists of taking derivatives in the $x_i$, dividing by polynomials in the $x_i$, and letting the symmetric group act on the $x_i$, in addition to linear operations. We see that this means we can apply the Dunkl operators to $F_a$ and check that the coefficient of $z^p$ in the result is $0$ to show that the Dunkl operators annihilate the $f_a$.
%
%We note that each $F_a$ is symmetric in the $x_i$ not including $x_a$, and that for any transposition $s_{ab} \in \Sigma_n$, $s_{ab}F_a=F_b$. Therefore we need only consider the action of the Dunkl operators on $F_0$. We also note that $\mathfrak{h}$ is spanned by $y_i-y_0$ for $0 < i \le n-1$; then using the fact that $F_0$ is symmetric in the $x_i$ with $i \ne 0$, we need only show that $(D_1-D_0)(F_0)$ has $z^p$ coefficient $0$ to show that all of the $f_a$ are annihilated by the Dunkl operators. 
%
%We also note that adding powers $z^k$ with $k > p$ will not change the value of the $z^p$ coefficient in $(D_1-D_0)(F_0)$. In particular, we note that since $x_0+\dots+x_{n-1}=0$ divides the coefficient of $z$ in $g$, we have $z^2 \mid g-1$. Then since $p>2$, we note that $z^{p+1} \mid z^{2p-2} \mid (g-1)^{p-1}$. Therefore we can add multiples of $(g-1)^{p-1}$ when taking the Dunkl operator's action on $F_0$, since even when multipled by another power series it cannot contribute anything to the coefficient of $z^p$. We also note that we can add $n$ times any multiple of $F_0$ since $n \equiv 0 \bmod p$.

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$ for all $0 \le i < n-1$. Let $F =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)$. Note that $F$ is symmetric and $F_a=\frac{F}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$:

\begin{align*}
\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F\right)\\
\end{align*}
%\begin{align*}
%&=V_i\frac{\partial}{\partial x_i}\left(\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\frac{\partial}{\partial x_i}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{i}^kz^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-1} -k\binom{c}{k}(-1)^kx_{n-1}^{k-1}z^k\right)+V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-1} k\binom{c}{k}(-1)^kx_{i}^{k-1}z^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{n-1}^{k-1}z^k\right)-V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=1}^{p-1} k\binom{c}{k}(-1)^{k-1}x_{i}^{k-1}z^k\right)\\
%&=V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)-\\&\;\;\;\;\;V_i\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} (k+1)\binom{c}{k+1}(-1)^{k}x_{i}^{k}z^{k+1}\right)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}\right)(1-x_{n-1}z)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}\right)(1-x_iz)\\
%&=\frac{V_i}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{n-1}^{k+1}z^{k+2}\right)-\\&\;\;\;\;\;\frac{V_i}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k+1}+ \sum_{k=0}^{p-2}c\binom{c-1}{k}(-1)^{k+1}x_{i}^{k+1}z^{k+2}\right)\\
%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{n-1}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left( \sum_{k=0}^{p-2} c\binom{c-1}{k}(-1)^{k}x_{i}^{k}z^{k}+ \sum_{k=1}^{p-1}c\binom{c-1}{k-1}(-1)^{k}x_{i}^{k}z^{k}\right)\\
%&=\frac{V_iz}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{n-1}^{k}z^{k}\right)-\\&\;\;\;\;\;\frac{V_iz}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}z^{p-1}+ \sum_{k=0}^{p-1} c\binom{c}{k}(-1)^{k}x_{i}^{k}z^{k}\right)\\
%&=F\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)+\\&\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\\&\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)
%\end{align*}
%
%Let $U=\frac{V_iz^p}{1-x_{n-1}z}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_i^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_{n-1}^{p-1}\right)-\frac{V_iz^p}{1-x_iz}\left( \sum_{k=0}^{p-1} \binom{c}{k}(-1)^kx_{n-1}^kz^k\right)\left(-c\binom{c-1}{p-1}(-1)^{p-1}x_i^{p-1}\right)$; clearly $z^p \mid U$ so all coefficients before that are $0$. The $z^p$ term is $\binom{c}{0}(-1)^0 $

Let $G_i=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right)$. Then $\frac{\partial F}{\partial x_i}=G_i+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F$.

We also see that:

\begin{align*}
\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_1}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_1}{1-x_0z}\\
\end{align*}

and that:

\begin{align*}
\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F+\frac{G_0}{1-x_0z}\\
&=\frac{z}{1-x_0z}F_0+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0+\frac{G_0}{1-x_0z}\\
\end{align*}

We note that $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$.
